Multisensor Architecture for an Intersection Management System

### 2015-03-27 ch2-mdf_ims.tex
Corrected typo

Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection, accidents prevention and security and surveillance systems. Those applications have to take into account some of the elements depicted in figure \ref{arch}, so developments in IMS have a wide range of approachesa and objectives. In order to organise and compare IMS applications, five components have been defined in which applications have their main focus, although mutiple components could be involved in the same development. In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them.

>>>>

Intersection monitoring is a required task to be done within intelligent transportation systems for high-level applications like traffic analysis, counting and classification of vehicles or pedestrians, event prediction, incident detection, accidents prevention and security and surveillance systems. Those applications have to take into account some of the elements depicted in figure \ref{arch}, so developments in IMS have a wide range of approaches and objectives. In order to study and compare IMS applications, five components have been defined in which applications have their main focus, although mutiple components could be involved in the same development. In figure  \ref{imsComps} a graph is presented, showing aforementioned components and elements within them.
